Reaction-Advection-Diffusion Models of Air Pollution

### 2024-04-25 paper.tex
3

\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{tikz}
\title{Reaction-Advection-Diffusion Models of Air Pollution}
\author{Daniel Henricks}

@@

>>>>

\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{tikz}
\title{Reaction-Advection-Diffusion Models of Air Pollution}
\author{Daniel Henricks}

@@

We also can set up a mass balance differential equation. The change of the abundance of a species must be equal to the sources less the sinks:

\begin{equation}
    \frac{dm}{dt} = F_{in} + E + P - F_{out} - L - D
\end{equation}

We need to represent the sinks using some loss rate. Let's assume that the losses are proportional to the amount of the species in the box, so the losses are
equal to $km$. (It turns out trivially that $k = \frac{1}{\tau}$). Let's also assume that the sources are independent of $m$. Then, we yield the ODE

\begin{equation}
    \frac{dm}{dt} = S - km
\end{equation}

which can be solved quite simply via separation of variables:

$$
    \frac{dm}{dt} = S - km
$$

$$
    \implies \int_0^t \frac{dm}{S-km} = \int_0^t dt
$$

$$
    \implies \frac{-1}{k} \ln{\abs{\frac{S-km(t)}{S-km(0)}}} = t
$$

$$
    \implies S - km(t) = Se^{-kt} - km(0)e^{-kt}
$$

\begin{equation}
    \implies m(t) = \frac{S}{k}(1-e^{-kt}) + m(0)e^{-kt}
\end{equation}

Finding the steady state of this equation yields $S_\infty = \frac{S}{k}$ (via taking the limit as $t \rightarrow \infty$).
